Probabilities of polar aligned disks in binary star systems

### 2024-06-05 src/tex/ms.tex
Add withs to figs
Compute polar fractions in examples

% Author list
\author{Ted Johnson}
%\affiliation{Department of Physics and Astronomy, University of Nevada, Las Vegas, 4505 South Maryland Parkway, Las Vegas, NV 89154, USA}
\author{Rebecca G. Martin}
%\affiliation{Department of Physics and Astronomy, University of Nevada, Las Vegas, 4505 South Maryland Parkway, Las Vegas, NV 89154, USA}
\author{Stephen Lepp}
\affiliation{Nevada Center for Astrophysics, University of Nevada, Las Vegas, 4505 South Maryland Parkway, Las Vegas, NV 89154, USA}
\affiliation{Department of Physics and Astronomy, University of Nevada, Las Vegas, 4505 South Maryland Parkway, Las Vegas, NV 89154, USA}

@@

\begin{figure}
    \begin{centering}
        \includegraphics{figures/sim_example.pdf}
        \caption{Example of system simulation and state determination. This figure tracks the orbital parameters
        of a massless third body orbiting a $1 M_\odot$ binary with equal mass stars and $e_b = 0.4$.
        Initially $\Omega = \frac{\pi}{2}$.
        Solid lines indicate
        the portion of the simulation that is required to determine the state. Dashed lines complete the evolution back to the system's
        initial conditions but are not needed for our analysis. In general, we will only integrate until the state of the system can be
        determined.}
        \label{fig:sim_example}
        \script{sim_example.py}
    \end{centering}
\end{figure}

@@

\begin{figure*}
    \begin{centering}
        \includegraphics{figures/mc_example.pdf}
        \caption{Monte Carlo results for a $1 M_\odot$ equal mass binary with $e_b=0.4$ for $j=0,0.5,1$. The position of each
        point shows the initial condition of the simulation, and the color denotes the dynamical state. Note that some are marked
        as ``unknown''. This is because we set a 1000 orbit limit on the integration for the sake of computational time.}
        \script{mc_example.py}
        \label{fig:mc}
    \end{centering}
\end{figure*}

@@

\begin{figure}
    \begin{centering}
        \includegraphics[options]{figures/compare_massive.pdf}
        \caption{
            Contour lines denoting solution boundaries found via the RKF method compared to MC results of the same conditions. Binary setup is the same
            as in Figure \ref{fig:mc}, but for $j=0.66$, which is its critical value \citep[see][]{martin2019,abod2022}. The grid here includes 250,000 points.
            There is some disagreement between RKF and {\sc REBOUND}, which we attribute to misclassification due to behavior on the orbital timescale (i.e. 
            small variations in $\Omega$ that cause the simulation to temporarily cross the $y$-axis twice, giving the false appearance of libration). \TJ{We can fix this}
        }
        \script{compare_massive.py}
        \label{fig:rkf}
    \end{centering}
\end{figure}

>>>>

% Author list
\author{Ted Johnson}
%\affiliation{Department of Physics and Astronomy, University of Nevada, Las Vegas, 4505 South Maryland Parkway, Las Vegas, NV 89154, USA}
\author{Rebecca G. Martin}
%\affiliation{Department of Physics and Astronomy, University of Nevada, Las Vegas, 4505 South Maryland Parkway, Las Vegas, NV 89154, USA}
\author{Stephen Lepp}
\affiliation{Nevada Center for Astrophysics, University of Nevada, Las Vegas, 4505 South Maryland Parkway, Las Vegas, NV 89154, USA}
\affiliation{Department of Physics and Astronomy, University of Nevada, Las Vegas, 4505 South Maryland Parkway, Las Vegas, NV 89154, USA}
\author{Stephen H. Lubow}
\affiliation{Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218, USA}

@@

\begin{figure}
    \begin{centering}
        \includegraphics[width=0.5\textwidth]{figures/sim_example.pdf}
        \caption{Example of system simulation and state determination. This figure tracks the orbital parameters
        of a massless third body orbiting a $1 M_\odot$ binary with equal mass stars and $e_b = 0.4$.
        Initially $\Omega = \frac{\pi}{2}$.
        Solid lines indicate
        the portion of the simulation that is required to determine the state. Dashed lines complete the evolution back to the system's
        initial conditions but are not needed for our analysis. In general, we will only integrate until the state of the system can be
        determined.}
        \label{fig:sim_example}
        \script{sim_example.py}
    \end{centering}
\end{figure}

@@

\begin{figure*}
    \begin{centering}
        \includegraphics[width=\textwidth]{figures/mc_example.pdf}
        \caption{Monte Carlo results for a $1 M_\odot$ equal mass binary with $e_b=0.4$ for $j=0,0.5,1$. The position of each
        point shows the initial condition of the simulation, and the color denotes the dynamical state. Note that some are marked
        as ``unknown''. This is because we set a 1000 orbit limit on the integration for the sake of computational time.}
        \script{mc_example.py}
        \label{fig:mc}
    \end{centering}
\end{figure*}

@@

\begin{figure}
    \begin{centering}
        \includegraphics[width=0.5\textwidth]{figures/compare_massive.pdf}
        \caption{
            Contour lines denoting solution boundaries found via the RKF method compared to MC results of the same conditions. Binary setup is the same
            as in Figure \ref{fig:mc}, but for $j=0.66$, which is its critical value \citep[see][]{martin2019,abod2022}. The grid here includes 250,000 points.
            There is some disagreement between RKF and {\sc REBOUND}, which we attribute to misclassification due to behavior on the orbital timescale (i.e. 
            small variations in $\Omega$ that cause the simulation to temporarily cross the $y$-axis twice, giving the false appearance of libration). \TJ{We can fix this}
            The MC result gives $f_{\text{polar}} = \variable{output/mc_out.txt}$ while the RKF result gives $f_{\text{polar}} = \variable{output/rk_out.txt}$ with
            numerical error on the order of $\variable{output/rk_err.txt}$.
        }
        \script{compare_massive.py}
        \label{fig:rkf}
    \end{centering}
\end{figure}
